Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-02-17 src/tex/ms.tex
removed redundant fig from appendix
Add reweighed kappa distributions
results text

\subsection{Relation to inclination}

@@

The event that shows the largest tension with $\kappa = 0$ is GW170818, for which $|\mu / \sigma| = \dots$ \mi{THOMAS: fill in these values}

We excluded GW200129 from the calculation of collective analysis.
Details of the exclusion are discussed in Sec.~\ref{sec:GW200129}.

\subsection{Bayesian hierarchical modeling}
% Corner plot of the mean and standard deviation of kappa
We then show the result of Bayesian hierarchical modeling in figure \ref{fig:corner_Gaussian}.
The median of $\mu$ within $90\%$ confidence interval is \variable{output/mu_median.txt}.
The median of $\sigma$ within $90\%$ confidence interval is \variable{output/sigma_median.txt}.
The posterior of $\mu$ is concentrated around $0$, which means the population constraint on $\kappa$ is consistent with GR.

@@

\begin{figure}[h]
    \script{birefringence_appendix.py}
    \includegraphics[width=\columnwidth]{figures/birefringence_appendix.pdf}
    \caption{The observed time domain signal with and without birefringence.}
    \label{fig:birefringence_appendix}
\end{figure}

@@

>>>>

\subsection{Relation to inclination}
\label{sec:inclination}

@@

The event that shows the largest tension with $\kappa = 0$ is GW170818, for which $|\mu / \sigma| = \dots$ \mi{THOMAS: fill in these values}
Additionally, the GW200129 result shows features that could be indicative of contamination from non-Gaussian instrumental noise, so we exclude it from the collective analysis.
We discuss both these events in detail below.

Another set of events stand out in Fig.~\ref{fig:violin_kappa} due evident bimodality in the $\kappa$ posterior.
That is the case for GW170104, GW190413\_134308, GW190521, GW190805\_211137, and GW191105\_143521.
\mi{THOMAS: can you list the total masses of these events?}
We understand this effect to be a consequence of the narrow sets of frequencies that are visible for these heavy events, as we mentioned in Sec.~\ref{sec:inclination} and further demonstrate below.

\subsection{Bayesian hierarchical modeling}

Figure \ref{fig:violin_kappa} shows some variance in the distribution of $\kappa$ posteriors, including some apparent outliers like GW170818.
This is not unexpected: assuming independent Gaussian noise, we might expect up to ${\sim}3$ events in a sample of 71 events to deviate from the true value of $\kappa$ by ${\sim}2\sigma$.
\mi{WIP}

% Corner plot of the mean and standard deviation of kappa
We then show the result of Bayesian hierarchical modeling in figure \ref{fig:corner_Gaussian}.
The median of $\mu$ within $90\%$ confidence interval is \variable{output/mu_median.txt}.
The median of $\sigma$ within $90\%$ confidence interval is \variable{output/sigma_median.txt}.
The posterior of $\mu$ is concentrated around $0$, which means the population constraint on $\kappa$ is consistent with GR.

@@

@@

\section{Reweighed kappa distributions}
\label{sec:reweighed_kappa}

\begin{figure}
    \script{reweighed_kappa.py}
    \includegraphics[width=\columnwidth]{figures/reweighed_kappa.pdf}
    \caption{Reweighed $\kappa$ distributions.}
    \label{fig:reweighed_kappa}
\end{figure}
